---
title: 'Peer-graded Assignment: Course Project: Shiny Application and Reproducible
  Pitch'
author: "Amit Kumar"
date: "June 26, 2017"
output:
  slidy_presentation: default
  beamer_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview and Web Application functionality: 
- This presentation is developed as part of a deliverable for the course "Developing Data Products" as part of the Coursera Data Science Specialization. The app developed for the first part of the assignment demo is available at: https://akumar555.shinyapps.io/car_mileage_prediction/ Source code for ui.R and server.R files are available on the GitHub repository: https://github.com/Amit1610/Shiny-Application-and-Reproducible-Pitch 
- The Application is useful to predict the Mileage of the cars if the specifications about the car is known/provided. The intended audience of this application may include people trying to understand the Fuel Economy or Mileage before making a purchase or rental decision. 
- I have used the Multiple Regression Model to predict the Miles per Gallon (MPG) based on the mtcars data, which is available and familiar to all the participants of Coursera Data Science Specialization Program. 
- I require you provide the Specifications of the car understand consideration and the application results in Prediction for "Miles Per Gallon" i.e., MPG for that car. You may choose your desire cars characteristic in term of : Cylinders, Displacement, Horse Power and Transmission etc.
- The result contains filters selected cars will show in a table on the main content with using the mtcars data-set from [R].

## Slide with R Output (Data Summary)

```{r, echo = TRUE}
summary(mtcars)
```

## Slide R Codes 

```{r, echo = FALSE}
my_data <- mtcars
my_data$cyl <- factor(my_data$cyl)
str(my_data)
require(ggpubr)
```

## Slide with Plots: 
These plots show the affects of car weight on the Mileage (Miles per Gallon, "MPG")

```{r, echo = FALSE}
ggscatter(my_data, x = "wt", y = "mpg",
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Weight (1000 lbs)", ylab = "Miles/ (US) gallon")
ggqqplot(my_data$mpg, ylab = "MPG")
ggqqplot(my_data$wt, ylab = "WT")
```


